A Meta-Analysis of Music Emotion Recognition Studies

### 2025-03-10 manuscript/_figure2.qmd
Added a template for compiling a pdf version of MS using apaquarto

```{r}
#| label: fig2
#| fig-width: 12
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest plot of the best valence models from all MER studies.

>>>>

```{r}
#| label: fig2
#| fig-width: 12
#| fig-height: 6
#| echo: false
#| warning: false
#| message: false
#| fig.cap: > 
#|   Forest plot of the best valence models from all MER studies.

### 2025-03-10 manuscript/_figure3.qmd
Added a template for compiling a pdf version of MS using apaquarto

```{r}
#| label: fig3
#| fig-width: 12
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest plot of the best arousal models from all MER studies.

>>>>

```{r}
#| label: fig3
#| fig-width: 12
#| fig-height: 6
#| warning: false
#| message: false
#| echo: false
#| fig.cap: > 
#|   Forest plot of the best arousal models from all MER studies.

### 2025-03-10 manuscript/_figure4.qmd
Added a template for compiling a pdf version of MS using apaquarto

```{r}
#| label: fig4
#| fig-width: 12
#| fig-height: 6
#| echo: false
#| fig.cap: > 
#|   Forest plot of the best classification models from all MER studies.

>>>>

```{r}
#| label: fig4
#| fig-width: 12
#| fig-height: 6
#| warning: false
#| message: false
#| echo: false
#| fig.cap: > 
#|   Forest plot of the best classification models from all MER studies.
